Implementation of a minimal branch-decomposition algorithm for simple planar graphs.

### 2024-05-27 paper/main.tex
Fix more grammar

	The rat-catching algorithm can be described as a game of two players, the rat and rat-catcher. Considering a graph $M$, the edges of a face can be thought of as walls of a room and vertices as the corners of some rooms. The rat moves from corner to corner along the walls and the rat-catcher moves from room to room through some wall. The rat-catcher can force the rat away from some walls by making noise. A round of this game is played with some noise-level $k$. The rat-catcher wins if they can force the rat to be in some wall of the room that they are in, with noise-level $k$, and the rat wins if there is a strategy whereby the rat can escape indefinitely.

@@

	For some noise-level and location of the rat-catcher, exactly which edges are noisy and which are quiet is definitions \ref{def:edge-quiet} and \ref{def:face-quiet}.

@@

	A quiet subgraph $Q(M, k, e)$, for some graph $M$, some noise-level $k$ and some $e \in E(M)$, is a subgraph of $M$ with $V(Q(M, k, e)) = V(M)$ and

@@

	\begin{problem}\label{problem:noisy-subgraph}
		Given a plane graph $M$ that might have parallel edges, an edge $e \in E(M)$, and noise-level $k \in \mathbb{N}$, output the quiet subgraph $Q(M, k, e)$.
	\end{problem}

@@

	The game states and possible moves, for some graph $M$ and some noise-level $k$, can be described as a graph $H(M, k)$.

@@

		The edges of the connected components are irrelevant for the rest of the algorithm, so only a list of vertices are returned for each connected component.

>>>>

	The rat-catching algorithm can be described as a game of two players, the rat and rat-catcher. Considering a graph $M$, the edges of a face can be thought of as walls of a room and vertices as the corners of some rooms. The rat moves from corner to corner along the walls and the rat-catcher moves from room to room through some wall. The rat-catcher can force the rat away from some walls by making noise. A round of this game is played with some noise level $k$. The rat-catcher wins if they can force the rat to be in some wall of the room that they are in, with noise level $k$, and the rat wins if there is a strategy whereby the rat can escape indefinitely.

@@

	For some noise level and location of the rat-catcher, exactly which edges are noisy and which are quiet are definitions \ref{def:edge-quiet} and \ref{def:face-quiet}.

@@

	A quiet subgraph $Q(M, k, e)$, for some graph $M$, some noise level $k$ and some $e \in E(M)$, is a subgraph of $M$ with $V(Q(M, k, e)) = V(M)$ and

@@

	\begin{problem}\label{problem:noisy-subgraph}
		Given a plane graph $M$ that might have parallel edges, an edge $e \in E(M)$, and noise level $k \in \mathbb{N}$, output the quiet subgraph $Q(M, k, e)$.
	\end{problem}

@@

	The game states and possible moves, for some graph $M$ and some noise level $k$, can be described as a graph $H(M, k)$.

@@

		The edges of the connected components are irrelevant for the rest of the algorithm, so only a list of vertices is returned for each connected component.
